---
title: "Server installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Server installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = F
)
```

## Pre-requisites
- sudo privlidges (or working with someone with privs)

## Create a new release of the bot
1. Do the usual pull, add, commit push workflow
2. Once you are happy with the changes and want to create a release at this point, figure out what release we are on. In the terminal type:
```{bash}
git tag
```

3. Create a lightweight tag of the next number in the sequence

Where version numbers typically follow the pattern of MAJOR.MINOR.PATCH (more info on [semantic versioning](https://semver.org/)) and incrementally adding versions as so:

    > MAJOR version when you make incompatible API changes,
    > MINOR version when you add functionality in a backwards compatible manner, and
    > PATCH version when you make backwards compatible bug fixes.

```{bash}
git tag #.#.#
```

4. Push the tag on to Github
```{bash}
git push origin --tags
```

5. Go to github and click `releases` (on the sidebar on the right hand side)
6. Click the `draft a new release` 
7. In the tag version space add the version you just created and add a description and title
8. Publish the release

For more info see the [Git basis -Tagging](https://git-scm.com/book/en/v2/Git-Basics-Tagging)

## Update and install awards bot on the server

1. sudo to the bot (screen -x if doing this collaboratively)
2. `curl -L paste-url-to-github-release-here`
3. Update R package on server
```{r}
install_github("NCEAS/awards-bot@version_number")
```

**Note** - the way this package is named is inconsistent - the package is call `awardsBot` while the repository is `awards-bot`

4. unzip the file:
```{bash}
unzip awards-bot-verion.zip
```

5. remove previous symlink:
```{bash}
rm awards-bot
```

6. Create new symlink:
```{bash}
ln -s awardsbot-version awards-bot
```

7. Create a copy of the current `main_cron_script.R` and name it using the current date
8. Copy the `main_cron_script.R` from awards-bot for the latest version
9. Check to see if the date is correct in the `LASTRUN` file
10. Do a test by just running `Rscript main_cron_script` (or copy the line from the crontab)
11. Un-comment out the line in the cron job if the script test is fine